### 2011-02-03 docs/architecture/architecture.tex
add more on base state arrays

\begin{figure}[tb]
\centering
\includegraphics[height=2.0in]{base_grid} \hspace{0.5in}
\includegraphics[height=2.0in]{base_spherical}
\caption{\label{Fig:base_state} (Left) For multi-level problems
  in planar geometry, we force a direct alignment between the radial
  array cell centers and the Cartesian grid cell centers by allowing
  the radial base state spacing to change with space and time.
  (Right) For multi-level problems in spherical geometry, since there
  is no direct alignment between the radial array cell centers and
  the Cartesian grid cell centers, we choose to fix the radial base
  state spacing across levels. Figure taken from~\cite{multilevel}}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=2.5in]{\archfigpath/mac2}
\hspace{0.1in}
\begin{minipage}[b]{3.8in}
\caption[The MAC grid]
{\label{fig:mac} The MAC grid for the velocity.  
Here the $x$-velocity is on the $x$-edges (shown as the 
blue points) and the $y$-velocity is on the $y$-edges
(shown as the red points).
}\ \\
\end{minipage}
\end{figure}

The MAC velocities are allocated at each level of refinement, {\tt n},
by making a \multifab\ array where each of the {\tt dm} components is
nodal in its respective direction:
\begin{verbatim}
  type(multifab) :: umac(dm)

  do comp=1,dm
     call multifab_build_edge(umac(n,comp), mla%la(n),1,1,comp)
  enddo
\end{verbatim}

@@

@@

To find the location of a particular species (for instance, ``carbon-12'')
in the allowed range of {\tt 1:nspec}, you do the following query:
\begin{verbatim}
  ic12 = network_species_index("carbon-12")
\end{verbatim}
If the resulting index is {\tt -1}, then the requested species was not
found.

>>>>

\begin{figure}[tb]
\centering
\includegraphics[height=2.0in]{base_grid} \hspace{0.5in}
\includegraphics[height=2.0in]{base_spherical}
\caption{\label{fig:base_state} (Left) For multi-level problems
  in planar geometry, we force a direct alignment between the radial
  array cell centers and the Cartesian grid cell centers by allowing
  the radial base state spacing to change with space and time.
  (Right) For multi-level problems in spherical geometry, since there
  is no direct alignment between the radial array cell centers and
  the Cartesian grid cell centers, we choose to fix the radial base
  state spacing across levels. Figure taken from~\cite{multilevel}}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=2.5in]{\archfigpath/mac2}
\hspace{0.1in}
\begin{minipage}[b]{3.8in}
\caption[The MAC grid]
{\label{fig:mac} The MAC grid for the velocity.  
Here the $x$-velocity is on the $x$-edges (shown as the 
blue points) and the $y$-velocity is on the $y$-edges
(shown as the red points).
}\ \\
\end{minipage}
\end{figure}

The MAC velocities are allocated at each level of refinement, {\tt n},
by making a \multifab\ array where each of the {\tt dm} components is
nodal in its respective direction:
\begin{lstlisting}[language={[95]fortran},mathescape=false]
  type(multifab) :: umac(dm)

  do comp=1,dm
     call multifab_build_edge(umac(n,comp), mla%la(n),1,1,comp)
  enddo
\end{lstlisting}

@@

The base state arrays are 2-dimensional, with the first dimension
giving the level in the AMR hierarchy and the second the radial index
into the base state.  For spherical geometries, the base state only
exists at a single level, so the first index will always be 1.  The
radial index is 0-based, to be consistent with the indexing for the
Cartesian state data.  For example, the base state density would be
dimensioned: {\tt rho0(nlevs,0:nr\_fine-1)}.  Here, {\tt nlevs} is the
number of levels of refinement and {\tt nr\_fine} is the number of
cells in the radial direction at the finest level of refinement.

For multilevel, plane-parallel geometry, all grids at the same height
will have the same resolution so that the full state data is always
aligned with the base state (see Figure~\ref{fig:base_state}).  Base
state data on coarse grids that are covered by fine grids is not
guaranteed to be valid.

For spherical problems, the base state resolution, $\Delta r$, is
generally picked to be finer than the Cartesian grid resolution,
$\Delta x$, i.e.\ $\Delta r < \Delta x$.  The ratio is controlled
by the parameter {\tt drdxfac}.

@@

To find the location of a particular species (for instance, ``carbon-12'')
in the allowed range of {\tt 1:nspec}, you do the following query:
\begin{lstlisting}[language={[95]fortran},mathescape=false]
  ic12 = network_species_index("carbon-12")
\end{lstlisting}
If the resulting index is {\tt -1}, then the requested species was not
found.
